`make.modifiers`

### 2023-07-07 inst/gitbook/03_make.modifiers.Rmd
Update 03_make.modifiers.Rmd

For example in the `speciation` part of a modifier, the default is to trigger an event from a uniform distribution and then check if that value is smaller than ($$speciation/(speciation + extinction)$$):

>>>>

For example in the `speciation` part of a modifier, the default is to trigger an event from a uniform distribution and then check if that value is smaller than ($speciation/(speciation + extinction)$):
